DNA Methylation Analyses

### 2023-02-17 DNA-methylation.Rmd
open authors
started adding references

---
title: 'DNA Methylation Analyses'
subtitle: '*Steven Roberts* and *Sam White* '
bibliography: DNA-Methylation.bib
---

@@

@@

# Generating files for downstream analysis

@@

>>>>

```{r,message = FALSE,echo = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc")
```

---
title: 'DNA Methylation Analyses'
subtitle: '*Steven Roberts*, *Sam White*, and ............ '
bibliography: DNA-Methylation.bib
---

@@

For a good review of epigenetic mechanisms including DNA methylation in marine organisms see @doi:10.1146/annurev-marine-010318-095114. @https://doi.org/10.1111/1755-0998.13542 offers a comparison of three methods for quantifying DNA methylation at single base-pair resolution using whole genome bisulfite sequencing (WGBS), reduced representation bisulfite sequencing (RRBS), and methyl-CpG binding domain bisulfite sequencing (MBDBS). The tutorial below is based on WGBS, though the general workflow would be consistent.

@@

# File Conversions

@@

# References
